Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-25 WSSSPE2_report/WSSSPE2_review.tex
Section 3.2: first draft.

According to Hong, costs of software-reliant research in the United Kingdom include
\textsterling 840 million of investment in the financial year 2013--2014, an
amount that has risen by 3\% on average over the past four years. About 30\% of
total research investment has been spent on research which relies on software
over the last four financial years. These numbers stemmed from an analysis of
data from $49,650$ grant titles and abstracts published on Gateway to Research
covering years 2010--2014.

Hong led the audience to ponder the questions of what we are going to \emph{do}
to help researchers and to achieve software sustainability if 92\% of
researchers and WSSSPE care about scientific software.
\begin{comment}
With apologies to Greg Wilson:
\href{http://software-carpentry.org/blog/2013/10/you-keep-using-that-word.html}
{You Keep Using That Word}
We can talk all day about the best ways of achieving sustainability
But what are we going to do to make it actually sustainable?
\end{comment}
Careers outside academic sector: 
Non-university Research (industry, government, etc.)
UK STEM graduate career paths: Early Career Research, Permanent Research Staff,
Professor.
The Scientific Century, Royal Society, 2010 (revised to reflect first stage
clarification from ``What Do PhD's Do?'' study.)
Who	are the people  we need to persuade?
What	 are	the incentives we need to put in place?
How are we going to show that the work we present here has benefit to the 92\%?
We are all the 92\%	and we can change the world if we	want!

>>>>

According to Hong, costs of software-reliant research in the United Kingdom included
\textsterling 840 million of investment in the financial year 2013--2014, an
amount that has risen by 3\% on average over the past four years. About 30\% of
total research investment has been spent on research which relies on software
over the last four financial years. These numbers stemmed from an analysis of
data from $49,650$ grant titles and abstracts published on Gateway to Research
between years 2010 and 2014.

Hong led the audience to ponder the following questions: What are we going to
\emph{do} to help and benefit software researchers and to achieve software
sustainability if~92\% of researchers and WSSSPE care about scientific software?
Who we need to persuade? What are the incentives we need to put in place? He
challenged the workshop participants to change the current deficient practices
in research and academia.
\begin{comment}
With apologies to Greg Wilson:
\href{http://software-carpentry.org/blog/2013/10/you-keep-using-that-word.html}
{You Keep Using That Word}
We can talk all day about the best ways of achieving sustainability
But what are we going to do to make it actually sustainable?

Careers outside academic sector: 
Non-university Research (industry, government, etc.)
UK STEM graduate career paths: Early Career Research, Permanent Research Staff,
Professor.
The Scientific Century, Royal Society, 2010 (revised to reflect first stage
clarification from ``What Do PhD's Do?'' study.)
Who	are the people  we need to persuade?
What	 are	the incentives we need to put in place?
How are we going to show that the work we present here has benefit to the 92\%?
We are all the 92\%	and we can change the world if we	want!
\end{comment}
